
## Simulation from slideshow

Here is a brief overview of the code in the slides shown in class:

Simulation Parameters and Setup:

n: Number of individuals in the dataset.
p: Number of covariates for each individual.
sweet_spot_range: A range of probabilities defining the "sweet spot" 

Treatment Assignment:

A binary treatment variable treated is assigned such that half the individuals receive the treatment (treated = 1), and the other half do not (treated = 0).

Simulating the Covariates:

covariates: A matrix of random normal variables representing individual characteristics.
beta: Coefficients for the covariates, drawn from a normal distribution.
Baseline Probability Calculation:

Logistic regression is used to calculate baseline probabilities of the outcome based on covariates.
Probabilities are constrained to the range [0, 1].
Sweet Spot Identification:

Individuals whose baseline probabilities fall within the defined sweet_spot_range are marked as being in the sweet spot (in_sweet_spot).
Outcome Probability Adjustment:

Treatment effects are modeled:
A base treatment effect (treatment_effect) is added for treated individuals.
An additional effect (sweet_spot_effect) is applied to treated individuals in the sweet spot.
Adjusted probabilities are capped at 1.
Outcome Simulation:

Outcomes are generated as binary random variables (outcome) based on the final probabilities (outcome_probs).
Result Compilation:

A list result compiles covariates, probabilities, treatment status, and outcomes for analysis.


```{r}
# Parameters
n <- 1000 # Number of individuals
p <- 5 # Number of covariates
sweet_spot_range <- c(0.4, 0.6)  # Sweet spot range for probabilities

# Generate a balanced treatment assignment
treated <- rep(c(0, 1), each = n / 2)

# Simulate covariates
covariates <- matrix(rnorm(n * p), nrow = n, ncol = p)

# Generate coefficients for covariates
beta <- rnorm(p)

# Compute baseline probabilities using logistic regression
baseline_probs <- 1 / (1 + exp(-covariates %*% beta))
baseline_probs <- pmin(pmax(baseline_probs, 0), 1)  # Keep probabilities in [0, 1]

# Identify individuals in the sweet spot
in_sweet_spot <- baseline_probs > sweet_spot_range[1] & baseline_probs < sweet_spot_range[2]

# Adjust probabilities for treated individuals
treatment_effect <- 0.05 # Base treatment effect
sweet_spot_effect <- 0.3 # Additional effect in sweet spot

outcome_probs <- baseline_probs
outcome_probs[treated == 1] <- outcome_probs[treated == 1] + treatment_effect
outcome_probs[treated == 1 & in_sweet_spot] <- outcome_probs[treated == 1 & in_sweet_spot] + sweet_spot_effect
outcome_probs <- pmin(outcome_probs, 1)  # Cap probabilities at 1
# Simulate outcomes
outcome <- rbinom(n, 1, prob = outcome_probs)
# Summary of the simulated data
result <- list(
  covariates = covariates,
  baseline_probs = baseline_probs,
  outcome_probs = outcome_probs,
  outcome = outcome,
  treated = treated,
  in_sweet_spot = in_sweet_spot
)


```

This chunk uses the sweetspot wrapper and plot_sweetspot function to display the results of the sweet spot analysis


```{r}
# Perform sweet spot analysis
result <- sweetspot(
  treated = treated,
  covariates = covariates,
  outcome = outcome,
  family = "binomial",         
  regularized = FALSE,         
  control_treated_ratio = 1    
)


# Plot the sweet spot
plot_sweetspot(result, "the sweetspot does not exist", title = "Sweet Spot Analysis on Simulated Data")

```


